\documentclass{exam}

\usepackage{tikz}
\usetikzlibrary{decorations.pathmorphing}

\pagestyle{headandfoot}
\firstpageheader{Name:\underline{\hspace{100pt}}}{}{Date:\underline{\hspace{100pt}}}
\runningheader{}{\textbf{The Aetherius Olympiad in Mathematics}}{}
\firstpagefooter{}{\thepage}{}
\runningfooter{}{\thepage}{}

\begin{document}

\begin{center}
	\LARGE{\textbf{The Aetherius Olympiad in Mathematics}}

	\vspace{8pt}

	\large{2024-09}
\end{center}

\section*{Instructions}

\begin{itemize}
	\item You must immediately fill out your name as well as the current date on the top of the page.
	\item You will be given 30 minutes to complete 3 questions. No extra time is allowed, and one must stop writing as soon as the time is up.
	\item One would be awarded marks based on not only the right answer, but also on the attempt, logic, and thought. A mere correct answer may not necessarily earn full marks.
	\item Scratch paper would be provided upon request. One may not use their own scratch paper.
	\item You may begin as soon as the timer starts.
\end{itemize}

\section*{Questions}

\begin{questions}
	\question[5]{
		There are two villages on one side of the river. One person from village A wants to go fishing at the river front, then go to village B to visit his friend. The direct distance from village A to the river is $250m$ and from village B to the river is $360m$. What is the minimum distance that person has to travel? Let the horizontal distance between A to B be $500m$.
		\begin{center}
			\begin{tikzpicture}
				\coordinate (LB) at (-1,-1);
				\coordinate (LT) at (-1,4.6);
				\coordinate (RB) at (6,-1);
				\coordinate (RT) at (6,4.6);
				\coordinate (Village A) at (0,2.5);
				\coordinate (Village B) at (5,3.6);

				\clip(LB)rectangle(RT);
				\fill[lime!70!olive] (LB)rectangle(RT); % background
				\pgfmathsetseed{14159}
				\draw[decorate, decoration={random steps, segment length=3mm, amplitude=1pt}, lime!70!black, line width=.5mm, double=cyan!60!white, double distance=1cm] (-1,1) -- (9,1); % river
				\draw[black, dotted] (Village A)--node[left]{$250m$}(0,1.6)--node[above]{$500m$}(5,1.6)--node[right]{$360m$}(Village B);
				\filldraw[black] (Village A) circle (2pt) node[anchor=south]{Village A};
				\filldraw[black] (Village B) circle (2pt) node[anchor=south]{Village B};
			\end{tikzpicture}
		\end{center}
	}
	\vspace{32em}
	\question[5]{$2024(2024^{2024})=?$

		Adapted from AMC12 2000 Problem 2
	}
	\vspace{32em}
	\question[5]{
		The Fibonacci sequence $1,1,2,3,5,8,13,21,\dots$ starts with two $1$'s, and each term afterwards is the sum of its two predecessors. Which one of the ten digits (1,2,3,4,5,6,7,8,9,0) is the last to appear in the units position of a number in the Fibonacci sequence?

		From AMC 12 2000 Problem 4
	}
	\vspace{32em}
	\question[5]{
		Two different prime numbers between $4$ and $18$ are chosen. When their sum is subtracted from their product, which of the following numbers could be obtained?

		From AMC 12 2000 Problem 6
	}
	\vspace{32em}
	\question[5]{
		How many positive integers $b$ have the property that $\log_{b} 729$ is a positive integer?

		From AMC12 2000 Problem 7
	}
	\vspace{32em}
\end{questions}

\end{document}
