\documentclass{exam}
\usepackage{tikz}
\usepackage{circuitikz}
\usepackage{subcaption}

\pagestyle{headandfoot}
\firstpageheader{Name:\underline{\hspace{100pt}}}{}{Date:\underline{\hspace{100pt}}}
\runningheader{}{\textbf{Kinematics}}{}
\firstpagefooter{The Aetherius Olympiad in Physics}{\thepage}{}
\runningfooter{The Aetherius Olympiad in Physics}{\thepage}{}

\begin{document}

\begin{center}
    \LARGE{\textbf{The Aetherius Olympiad in Physics}}

    \vspace{8pt}

    \large{2023-11}
\end{center}

\section*{Instructions}
\begin{itemize}
    \item You must immediately fill out your name as well as the current date on the top of the page.
    \item You will be given 30 minutes to complete 3 questions. No extra time is allowed, and one must stop writing as soon as the time is up.
    \item You will have to show adequate work to prove that your answer was the result of thoughts but not guesses or anything else.
    \item You must explicitly indicate what your final answer is (\textit{e.g.} circling, boxing, etc).
    \item All questions would be scored out of 5, and one would receive scores based on not only the right answer, but also on the attempt, logic, and thought. A mere correct answer may not necessarily earn full marks.
    \item Scratch paper would be provided upon request. One may not use their own scratch paper.
    \item You may begin as soon as the timer starts.
\end{itemize}

\section*{Questions}

\begin{questions}
    \question[3]{Using dimensional analysis, find the dimensions for $ k $ (Coulomb constant), $ h $ (Planck constant), and the $ \epsilon_0 $ (vacuum electric permittivity)}.

    \pagebreak

    \question[3]{Given that area $ [A] = [k]^\alpha [h]^\beta [\epsilon_0]^\gamma $, find $ \alpha $, $ \beta $, and $ \gamma $.}

    \pagebreak

    \question[5]{Given that $ ?^\alpha = [k]^\beta [h]^\gamma [\epsilon_0]^\delta $, find $ \alpha $, $ \beta $, and $ \gamma $, where $ \alpha = 202311 $, $ \beta = 202311 $, $ \gamma = -202311 $, and $ \delta = 0 $, find $ ? $.}
\end{questions}

\end{document}